Figures for conference paper

### 2019-04-24 conference figures.Rmd
update flowchart

```{r}
test <- grViz("digraph flowchart {

@@

      # Ouput
      subgraph cluster2 {
      label = 'System Output';
      style = filled;
		  color = lightCyan;
		  node [style = filled, color = black, fillcolor = white];
      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings \n and Preparatory Coursework']
      }

      # Intermediate nodes
      node [color = black]
      TM [label = 'Topic Model']
      TE [label = 'Student큦 Topic Expertise']
      AI [label = 'Student큦 Academic Interests']
      AP [label = 'Student큦 Academic Performance']
      PM [label = 'Predictive Models']
      GP [label = 'Grade Prediction']
      TR [label = 'Student큦 Transcript']

      # edges
      {TE, KW} -> AI; 
      {ID, SD} -> TR;
      TR -> AP;
      {TR, TM} -> TE;
      {PM, TE, AP, CS} -> GP;
      GP -> WAR;

      edge[label = 'LDA']
      CD -> TM;

@@

      edge[label = 'KL distance']
      {TM, AI} -> SUG
      }
      ")

>>>>

```{r}
grViz("digraph flowchart {

@@

      # Ouput
      subgraph cluster2 {
      label = 'System Output';
      style = filled;
		  color = lightCyan;
		  node [style = filled, color = black, fillcolor = white];
      rank = same;
      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings']
      PRE [label = 'Preparatory Coursework']
      }

      # Intermediate nodes
      node [color = black]
      TM [label = 'Topic Model']
      TE [label = 'Student큦 Topic Expertise']
      AI [label = 'Student큦 Academic Interests']
      AP [label = 'Student큦 Academic Performance']
      PM [label = 'Predictive Models']
      GP [label = 'Grade Prediction']
      TR [label = 'Student큦 Transcript']
      x [shape=circle,width=.01,height=.01,label='']

      # edges

      WAR SUG PRE [ group = 1 ]

      {TE, KW} -> AI; 
      {ID, SD} -> TR;
      TR -> AP;
      {TR, TM} -> TE;
      {PM, TE, AP, CS} -> GP;
      GP -> WAR;
		  {TM, PM, WAR} -> PRE;

      edge[label = 'LDA', decorate = TRUE]
      CD -> TM;

@@

      edge[label = '']
      {TM, AI} -> x [arrowhead=none]
      edge[label = 'KL distance', decorate = TRUE]
      x -> SUG;

      }
      ")
